What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
small change

We gather a test suite of 91 formulas used in real-world requirement specification. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples \cite{RV10}. We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification. % We choose to visualize each formula specifically, rather than complete specifications, as

We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$. Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of. We are able to generate tractable visualization on the $85$, or over $93\%$, of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.

>>>>

We gather a test suite of 91 formulas used in real-world requirement specification. We take $6$ specifications from NASA's Automated Airspace Concept (AAC)\cite{GCMTR16}. We also collect formulas from the Acacia suite of examples \cite{RV10}. We reap $85$ formulas from the suite of $23$ examples, by generating separate visualizations for each line of specification. We choose to visualize each formula specifically, rather than complete specifications, as complete specifications may describe large complex systems, and we only intend the use case of validating individual specification formulas. % We choose to visualize each formula specifically, rather than complete specifications, as

We run \texttt{ltl2regex} on these $91$ examples, the tool completes execution (within timeout of $20$s) on $87$. Within the $87$, two examples have regular expressions of star height $8$ and are intractable to generate graph visualizations of. We are able to generate tractable visualization on the remaining $85$, or over $93\%$ of benchmarks tested. The plots of visualization complexity on these formula are provided below in \cref{fig:real-world}.
